A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-08-13 Papers/Paper/manuscript.Rmd
add appendix graph and table

>>>>

# Appendix C

```{r gam-linearity-table}

gam_linear <- read_rds(here("Analysis/models/gams_linearity_test.rds")) %>% 
  mutate(Term=factor(Term, 
                        levels=c("s(surprisal)",
                                 "ti(freq)",
                                 "ti(len)",
                                 "s(prev_surp)",
                                 "ti(prev_freq)",
                                 "ti(prev_len)",
                                 "(Intercept)",
                                 "surprisal",
                                 "prev_surp"
                                 )
                                 )) %>% 
  arrange(Term) %>% filter(Term %in% c("s(surprisal)", "s(prev_surp)", "surprisal","prev_surp")) %>% 
  mutate(Term=c("Spline Surprisal", "Spline Past Surprisal", "Linear Surprisal", "Linear Past Surprisal"))

knitr::kable(gam_linear, format="latex", position="ht",caption="Comparison of significances for linear and spline terms of suprisals from a GAM. We fit GAM models with current and past word surprisal as parametric terms, current and past word surprisal and spline terms, and current and past frequence and length as tensors to predict reading time. Here we show the estimated pvalues for the linear and spline surprisal terms at current and past words. The spline terms account for any non-linear surprisal effects.") %>%   kable_styling(font_size = 10)

# Appendix D
(ref:gam-grid) CAPTION GOES HERE

```{r gam-grid, out.height="100%",  fig.pos="ht", fig.cap="(ref:gam-grid)"}

knitr::include_graphics(here("Analysis/models/gam_grid.png"))
